Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-04-11 analysis/paper/paper.Rmd
Figure creation and writing

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 2,
  comment = "#>",
  fig.path = "../figures/",
  dev="png"
)
```

@@

```{r burialestimate, fig.cap="Relationship between known interments, counts of pithoi, and counts of pithoi, amphorae and kraters. The straight line represents the mean estimate based on these three values."}

@@

library(ggpubr)
library(cowplot)
library(gridExtra)
library(ineq)
library(ggrepel)
library(reshape)
library(data.table)
library(extrafont)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
font_import(paths="../paper/font",pattern="GARA")
loadfonts(device="win")

#The data from the tomb database are added, and 'attached' so that the variables therein need no longer be referred to in their long format (i.e. 'tombs$total_pottery' becomes simply 'total_pottery')

@@

colnames(aorist_all_tombs)<-c("aoristic_sum")
dates<-seq(from = 610, to = 1100, by = 10)
dates<-rev(dates)
row.names(aorist_all_tombs)<-dates
aorist_all_tombs<-data.frame(aorist_all_tombs)
setDT(aorist_all_tombs, keep.rownames = "decade")
aorist_all_tombs$decade<-as.numeric(aorist_all_tombs$decade)

@@

aorist_tomb_values<-tomb_dates_aorist[16:65]
aorist_tomb_matrix<-data.matrix(aorist_tomb_values)
aorist_tomb_matrix[aorist_tomb_matrix == 0] <- NA
aorist_tomb_dates$medians<-apply(aorist_pot_matrix,2,median,na.rm=TRUE)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 2,
  comment = "#>",
  fig.path = "../figures/",
  dev="png"
)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(ineq)
library(ggrepel)
library(reshape)
library(data.table)
library(extrafont)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
font_import(paths="../paper/font",pattern="GARA")
loadfonts(device="win")

@@

```{r burialestimate, fig.dim = c(7, 4), dpi=300, fig.align='center', fig.cap="Relationship between known interments, counts of pithoi, and counts of pithoi, amphorae and kraters. The straight line represents the mean estimate based on these three values."}

@@

@@

colnames(aorist_all_tombs)<-c("aoristic_sum")
dates<-seq(from = 1100, to = 610, by = -10)
row.names(aorist_all_tombs)<-dates
aorist_all_tombs<-data.frame(aorist_all_tombs)
setDT(aorist_all_tombs, keep.rownames = "decade")
aorist_all_tombs$decade<-as.numeric(aorist_all_tombs$decade)

@@

aorist_tomb_values<-tomb_dates_aorist[16:65]
aorist_tomb_matrix<-data.matrix(aorist_tomb_values)
aorist_tomb_matrix[aorist_tomb_matrix == 0] <- NA
aorist_tomb_dates$medians<-apply(aorist_tomb_matrix,2,median,na.rm=TRUE)
